Quantifying Lewontin's Paradox Suggests Natural Selection is Unlikely to Explain the Narrow Range of Diversity Among Species

### 2021-06-05 manuscript/elife/elife-manuscript.tex
more elife formatting, fig data

\begin{figure}
  \includegraphics[width=0.7\linewidth]{figures/Nc_figure.pdf}
  \caption{The distribution of approximate census population sizes estimated by this
   study. Some phyla containing few species were excluded for clarity.}
   \label{fig:figure-nc}

   \figsupp[The relationship between body mass and population density found by
   \cite{Damuth1987-sg}, which is used to predict population densities.]{The
     source of this data is appendix table of \cite{Damuth1987-sg}; the color
     indicates Damuth's original group labels. The dashed line was estimated
     using a lognormal regression model in Stan. References to each measurement
   are available in \cite{Damuth1987-sg}.}{\includegraphics[]{figures/damuth.pdf}}\label{figsupp:damuth}

  \figsupp[The fraction of total species on earth included in this study's
  sample, per class.]{The color of the points represents phylum, and the size of
the point represents the absolute number of species by
class.}{\includegraphics{figures/species_counts.pdf}}\label{figsupp:species-counts}

\figsupp[Validation of this paper's range estimates procedure against the IUCN Red List's range estimates.]{
  The correspondence between the ranges estimated with the alpha hull
  method applied to GBIF data used in this paper and IUCN Red List's Extent
  of Occurrence for the subset of species in both datasets. Note that the
  IUCN Red List contains predominantly endangered species, which leads to
  ascertainment bias; still, the high correlation between the estimated
ranges shows the alpha hull method works well.}{\includegraphics[]{figures/iucn_redlist_ranges.pdf}}\label{figsupp:redlist-ranges}

\figsupp[Validation of this paper's range estimates against the categorical labels of \cite{Leffler2012-zj}.]{
  The estimated ranges using GBIF occurrence data, ordered within and
  colored by the original range category labels assigned in
\cite{Leffler2012-zj}.}{\includegraphics[]{figures/range_categories.pdf}}\label{figsupp:range-cats}

  \figsupp[The relationship between body length (meters) and body mass (grams)
  in the \cite{Romiguier2014-bp} data set.]{The relationship between body
    length (meters) and body mass (grams) in the \cite{Romiguier2014-bp} data
    set. This is used to infer body masses for taxa. The gray dashed line is the
  line of best fit inferred using
Stan.}{\includegraphics[]{figures/body_mass_length.pdf}}\label{figsupp:body-mass-length}

@@

\begin{figure}
  \begin{fullwidth}
  \includegraphics[width=\linewidth]{figures/diversity_popsize_full.pdf}

@@

    \figsupp{A linear-log version of Figure 2. Points are colored by phylum,
      and the shaded region is the predicted neutral level of diversity
      assuming $N_e = N_c$ with mutation range ranging between $10^{-10} \le
    \mu \le 10^{-8}$.}{\includegraphics[width=\textwidth]{figures/diversity_popsize_linear.pdf}}\label{figsupp:popsize-linear}

      \figsupp{A version of Figure 2 with OLS estimates per phylum. Diversity
      and approximate population size for 172 taxa, colored by phylum; the
    dashed lines indicate the non-phylogenetic OLS estimates of the
  relationship between population size and diversity grouped by
phyla.}{\includegraphics[width=\textwidth]{figures/diversity_popsize_averages.pdf}}\label{figsupp:popsize-ave}

  \figsupp{The posterior distributions and fitted relationship between
    diversity and both body mass and range size. The relationship between
    diversity (differences per basepair) and body mass (left) and range (right)
    across 172 species. The top row are posterior distributions of parameters
    estimated using the phylogenetic mixed-effects model using 166 taxa in the
    synthetic phylogeny for the intercept, slope, and phylogenetic signal from
    the mixed-effects model. The bottom row contain each species as a point,
    colored by phyla. The gray dashed line is the non-phylogenetic standard
    regression estimate, and the blue dashed line is the relationship fit by
    the phylogenetic mixed-effects
  model.}{\includegraphics[width=\textwidth]{figures/diversity_range_bodymass.pdf}}\label{figsupp:div-range-bodymass}

   \figsupp{Pairwise diversity grouped by the range categories from
    \cite{Leffler2012-zj}, with point size indicating the predicted population
    density. The vertical lines are the range category group
  means.}{\includegraphics{figures/diversity_leffler_ranges.pdf}}\label{figsupp:div-leffler}
  \end{fullwidth}
\figdata{The diversity and population size dataset for 172 metazoan taxa.}
\end{figure}

@@

\begin{figure}
  \begin{fullwidth}
  \includegraphics[width=\linewidth]{figures/diversity_pcm.pdf}

@@

  \figsupp{The posterior distributions for the parameters of the phylogenetic
    mixed-effects model of diversity and population size (this is analogous to
    Figure \FIG{pcm}B) fit separately on chordates ($n=68$), molluscs
    ($n=13$), and arthropods ($n=68$). The phylogenetic mixed-effects model for
    chordates indicated the best-fitting model had no residual variance
    ($\sigma_r^2 = 0$), so an alternate model without this variance component
    was used to ensure proper convergence; this model is shown in green.
    The light blue (green) shaded regions are the 90\% credible intervals, the
    blue (green) lines the posterior averages, the gray shaded regions the OLS
    bootstrap 95\% confidence intervals, and the gray lines the OLS estimate.
    Note that unlike \FIG{pcm}, the OLS estimate uses all taxa,
    not just those present in the phylogeny, since splitting the data by phyla
    reduces sample sizes (OLS with just the subset of taxa in the phylogeny is
    not significant for either chordates and arthropods). The vertical dashed
  gray line indicates zero.}{\includegraphics[width=\textwidth]{figures/div_popsize_post_phyla.pdf}}\label{figsupp:div-popsize-post-phyla}

  \figsupp{The ancestral continuous trait estimates for diversity and population size with species labels.}{\includegraphics[width=\textwidth]{figures/biconmap_diversity.pdf}}\label{figsupp:anc-species}

  \figsupp{The ancestral continuous trait estimates for recombination map
  length and diversity and population size with species
labels.}{\includegraphics[width=\textwidth]{figures/biconmap.pdf}}\label{figsupp:anc-maplen}

@@

\begin{figure}[t!]
  \begin{fullwidth}
  \includegraphics[width=\linewidth]{figures/figure_3.pdf}

@@

  \figsupp{The relationship between genome size and approximate census
    population size. The dashed gray line indicates the OLS fit. Tiger
    salamander (\emph{Ambystoma tigrinum}) was excluded because of its
  exceptionally large genome size (~30Gbp).}{\includegraphics[width=\textwidth]{figures/genome_size_popsize.pdf}}\label{figsupp:genome-size-Nc}

  \figsupp{The relationship between genome size and recombination map length.
    The dashed gray line indicates the OLS fit for all taxa, and the dashed
    colored dashed lines indicate the linear relationship fit by phyla. Tiger
    salamander (\emph{Ambystoma tigrinum}) was excluded because of its
  exceptionally large genome size (~30Gbp).}{\includegraphics[width=\textwidth]{figures/genome_size_maplength.pdf}}\label{figsupp:genome-size-maplen}

  \figsupp[The relationship between $N_c$ and diversity in the
    \cite{Corbett-Detig2015-gt} data, and the relationship between estimated
    reduction in diversity and census size, for three different approaches.]{(A)
    The diversity data from \cite{Corbett-Detig2015-gt} and the census
    population size estimated here for metazoan taxa. (B) The reductions in
    diversity, $R = \nicefrac{N_e}{N}$, plotted against census size across
    species. The red points are the reductions estimated by
    \cite{Corbett-Detig2015-gt}. This confirms
    \citeauthor{Corbett-Detig2015-gt}'s (2015) finding that the impact of
    selection ($I = 1-R$) increases with census population size (though, in the
    original paper size body size and range were used as separate proxy
    variables for census population size). The green and red points are the
    predicted reduction in diversity under the recurrent hitchhiking (RHH) and
    background selection (BGS) model using the \emph{Drosophila melanogaster}
    parameters as described in the main text.  The reduction in the diversity
    due to sweeps, from Equation 1, is determined by the term
    $2NS$.  Green points treat $N$ as the implied effective population size
    from diversity $\widetilde{N}_e = \nicefrac{\widehat{\pi}}{4\mu}$, assuming
    $\mu = 10^{-9}$. Yellow points treat $N$ as the census size, $N = N_c$.
    Overall, using the census size, e.g.  $2N_cS$, leads to reductions in
    diversity that far exceed the empirical estimates of Corbett-Detig et al.
  and reasonable model-based predictions from
$\widetilde{N}_e$.}{\includegraphics[width=\textwidth]{figures/corbett_detig.pdf}}\label{figsupp:reductions}

\figsupp{Comparison of the \emph{Drosophila} sweep parameters used in this study with parameters from other studies.
     (A) The estimate of the number of sweeps per basepair, per genome
      ($\nu_\text{BP}$) from Table 2 of \cite{Elyashiv2016-vt} (the studies
      included are \cite{Li2006-xa,Andolfatto2007-uy,Macpherson2007-qt} and
      \cite{Jensen2008-vz}); the red point is my estimate used in
      this paper. (B) Points are the data from \cite{Shapiro2007-gp}.  The
      blue line is the non-linear least squares fit to the data, and the green
      dashed line is the sweep model parameterized by the genome-wide average
      sweep coalescent rate $2NS \approx 0.92$ from the classic sweep and
      background selection model of \cite{Elyashiv2016-vt} ($r_s$ in
    Supplementary Table S6).}{\includegraphics[width=\textwidth]{figures/linked_sel_params.pdf}}\label{figsupp:linked-sel-params}

@@

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=\textwidth]{figures/diversity_popsize_linear.pdf}
%   % figure 2-supplement 1
%   \figsupp{A version of Figure \ref{fig:figure-1} with diversity on a linear,
%     rather than log, scale. Points are colored by phylum, and the shaded region
%     is the predicted neutral level of diversity assuming $N_e = N_c$ with mutation
%   range ranging between $10^{-10} \le \mu \le 10^{-8}$. }

%   \label{suppfig:figure-1-linear}
% \end{figure}

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=\textwidth]{figures/diversity_popsize_averages.pdf}
%   % figure 2-supplement 2
%   \figsupp{Diversity and approximate population size for 172 taxa, colored by
%     phylum; the dashed lines indicate the non-phylogenetic OLS estimates of the
%   relationship between population size and diversity grouped by phyla.}

%   \label{suppfig:figure-1-ave}
% \end{figure}

% \begin{figure}[!htb] \centering
%   \includegraphics[width=\textwidth]{figures/diversity_range_bodymass.pdf}
%   % figure 2-supplement 3
%   \figsupp{The relationship between diversity (differences per basepair) and
%     body mass (left) and range (right) across 172 species. The top row are
%     posterior distributions of parameters estimated using the phylogenetic
%     mixed-effects model using 166 taxa in the synthetic phylogeny for the
%     intercept, slope, and phylogenetic signal from the mixed-effects model. The
%     bottom row contain each species as a point, colored by phyla. The gray
%     dashed line is the non-phylogenetic standard regression estimate, and the
%     blue dashed line is the relationship fit by the phylogenetic mixed-effects
%   model. }

%   \label{suppfig:figure-div-range-bodymass}
% \end{figure}

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=\textwidth]{figures/div_popsize_post_phyla.pdf}
%   % figure 3-supplement 1
%   \figsupp{The posterior distributions for the parameters of the phylogenetic
%     mixed-effects model of diversity and population size (this is analogous to
%     Figure \ref{fig:figure-2}B) fit separately on chordates ($n=68$), molluscs
%     ($n=13$), and arthropods ($n=68$). The phylogenetic mixed-effects model for
%     chordates indicated the best-fitting model had no residual variance
%     ($\sigma_r^2 = 0$), so an alternate model without this variance component
%     was used to ensure proper convergence; this model is shown in green.
%     The light blue (green) shaded regions are the 90\% credible intervals, the
%     blue (green) lines the posterior averages, the gray shaded regions the OLS
%     bootstrap 95\% confidence intervals, and the gray lines the OLS estimate.
%     Note that unlike Figure \ref{fig:figure-2}, the OLS estimate uses all taxa,
%     not just those present in the phylogeny, since splitting the data by phyla
%     reduces sample sizes (OLS with just the subset of taxa in the phylogeny is
%     not significant for either chordates and arthropods). The vertical dashed
%   gray line indicates zero.}

%   \label{suppfig:div_popsize_post_phyla}
% \end{figure}

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=\textwidth]{figures/biconmap_diversity.pdf}
%   % figure 3-supplement 2
%   \figsupp{}
%   \label{suppfig:biconmap_diversity}
% \end{figure}

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=\textwidth]{figures/biconmap.pdf}
%   % figure 3-supplement 3
%   \figsupp{}
%   \label{suppfig:biconmap}
% \end{figure}

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=\textwidth]{figures/genome_size_popsize.pdf}
%   % figure 4-supplement 1
%   \figsupp{The relationship between genome size and approximate census
%     population size. The dashed gray line indicates the OLS fit. Tiger
%     salamander (\emph{Ambystoma tigrinum}) was excluded because of its
%   exceptionally large genome size (~30Gbp).}

%   \label{supfig:genome_size_popsize}
% \end{figure}

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=\textwidth]{figures/genome_size_maplength.pdf}
%   % figure 4-supplement 2
%   \figsupp{The relationship between genome size and recombination map length.
%     The dashed gray line indicates the OLS fit for all taxa, and the dashed
%     colored dashed lines indicate the linear relationship fit by phyla. Tiger
%     salamander (\emph{Ambystoma tigrinum}) was excluded because of its
%   exceptionally large genome size (~30Gbp).}
%   \label{supfig:genome_size_maplength}
% \end{figure}

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=\textwidth]{figures/corbett_detig.pdf}
%   % figure 4-supplement 1
%   \figsupp{(A) The diversity data from \textcite{Corbett-Detig2015-gt} and the
%     census population size estimated here for metazoan taxa. (B) The
%     reductions in diversity, $R = \nicefrac{N_e}{N}$, plotted against census
%     size across species. The red points are the reductions estimated by
%     \textcite{Corbett-Detig2015-gt}. This confirms
%     \citeauthor{Corbett-Detig2015-gt}'s (2015) finding that the impact of
%     selection ($I = 1-R$) increases with census population size (though, in the
%     original paper size body size and range were used as separate proxy
%     variables for census population size). The green and red points are the
%     predicted reduction in diversity under the recurrent hitchhiking (RHH) and
%     background selection (BGS) model using the \emph{Drosophila melanogaster}
%     parameters as described in the main text.  The reduction in the diversity
%     due to sweeps, from Equation \eqref{eqn:div}, is determined by the term
%     $2NS$.  Green points treat $N$ as the implied effective population size
%     from diversity $\widetilde{N}_e = \nicefrac{\widehat{\pi}}{4\mu}$, assuming
%     $\mu = 10^{-9}$. Yellow points treat $N$ as the census size, $N = N_c$.
%     Overall, using the census size, e.g.  $2N_cS$, leads to reductions in
%     diversity that far exceed the empirical estimates of Corbett-Detig et al.
%   and reasonable model-based predictions from $\widetilde{N}_e$.}
%   \label{suppfig:corbett_detig}
% \end{figure}

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=\textwidth]{figures/linked_sel_params.pdf}
%   % figure 4-supplement 2
%   \caption{(A) The estimate of the number of sweeps per basepair, per genome
%     ($\nu_\text{BP}$) from Table 2 of \textcite{Elyashiv2016-vt} (the studies
%     included are \cite{Li2006-xa,Andolfatto2007-uy,Macpherson2007-qt} and
%     \cite{Jensen2008-vz}); the red point is my estimate used in
%     this paper. (B) Points are the data from \textcite{Shapiro2007-gp}.  The
%     blue line is the non-linear least squares fit to the data, and the green
%     dashed line is the sweep model parameterized by the genome-wide average
%     sweep coalescent rate $2NS \approx 0.92$ from the classic sweep and
%   background selection model of \textcite{Elyashiv2016-vt} ($r_s$ in
% Supplementary Table S6).}

%   \label{suppfig:linked-sel-params}
% \end{figure}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{figures/diversity_popsize_redlist.pdf}
  \captionof{figure}{A version of \FIG{pi-Nc} with points colored by their
    IUCN Red List conservation status. Margin boxplots show the diversity and
    population size ranges (thin lines) and interquartile ranges (thick lines)
    for each category. NA/DD indicates no IUCN Red List entry, or Red List
  status Data Deficient; LC is Least Concern, NT is Near Threatened, VU is
Vulnerable, EN is Endangered, and CR is Critically Endangered.}
\label{figsupp:figure-1-redlist}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=0.7\linewidth]{Nc_figure.pdf}
  \caption{The distribution of approximate census population sizes estimated by this
   study. Some phyla containing few species were excluded for clarity.}
   \label{fig:figure-nc}

   \figsupp[The relationship between body mass and population density found by
   \cite{Damuth1987-sg}, which is used to predict population densities.]{The
     source of this data is appendix table of \cite{Damuth1987-sg}; the color
     indicates Damuth's original group labels. The dashed line was estimated
     using a lognormal regression model in Stan. References to each measurement
   are available in \cite{Damuth1987-sg}.}{\includegraphics[]{damuth.pdf}}\label{figsupp:damuth}

  \figsupp[The fraction of total species on earth included in this study's
  sample, per class.]{The color of the points represents phylum, and the size of
the point represents the absolute number of species by
class.}{\includegraphics{species_counts.pdf}}\label{figsupp:species-counts}

\figsupp[Validation of this paper's range estimates procedure against the IUCN Red List's range estimates.]{
  The correspondence between the ranges estimated with the alpha hull
  method applied to GBIF data used in this paper and IUCN Red List's Extent
  of Occurrence for the subset of species in both datasets. Note that the
  IUCN Red List contains predominantly endangered species, which leads to
  ascertainment bias; still, the high correlation between the estimated
ranges shows the alpha hull method works well.}{\includegraphics[]{iucn_redlist_ranges.pdf}}\label{figsupp:redlist-ranges}

\figsupp[Validation of this paper's range estimates against the categorical labels of \cite{Leffler2012-zj}.]{
  The estimated ranges using GBIF occurrence data, ordered within and
  colored by the original range category labels assigned in
\cite{Leffler2012-zj}.}{\includegraphics[]{range_categories.pdf}}\label{figsupp:range-cats}

  \figsupp[The relationship between body length (meters) and body mass (grams)
  in the \cite{Romiguier2014-bp} data set.]{The relationship between body
    length (meters) and body mass (grams) in the \cite{Romiguier2014-bp} data
    set. This is used to infer body masses for taxa. The gray dashed line is the
  line of best fit inferred using
Stan.}{\includegraphics[]{body_mass_length.pdf}}\label{figsupp:body-mass-length}

@@

\begin{figure}
  \begin{fullwidth}
  \includegraphics[width=\linewidth]{diversity_popsize_full.pdf}

@@

    \figsupp{A linear-log version of Figure 2. Points are colored by phylum,
      and the shaded region is the predicted neutral level of diversity
      assuming $N_e = N_c$ with mutation range ranging between $10^{-10} \le
    \mu \le 10^{-8}$.}{\includegraphics[width=\textwidth]{diversity_popsize_linear.pdf}}\label{figsupp:popsize-linear}

      \figsupp{A version of Figure 2 with OLS estimates per phylum. Diversity
      and approximate population size for 172 taxa, colored by phylum; the
    dashed lines indicate the non-phylogenetic OLS estimates of the
  relationship between population size and diversity grouped by
phyla.}{\includegraphics[width=\textwidth]{diversity_popsize_averages.pdf}}\label{figsupp:popsize-ave}

  \figsupp{The posterior distributions and fitted relationship between
    diversity and both body mass and range size. The relationship between
    diversity (differences per basepair) and body mass (left) and range (right)
    across 172 species. The top row are posterior distributions of parameters
    estimated using the phylogenetic mixed-effects model using 166 taxa in the
    synthetic phylogeny for the intercept, slope, and phylogenetic signal from
    the mixed-effects model. The bottom row contain each species as a point,
    colored by phyla. The gray dashed line is the non-phylogenetic standard
    regression estimate, and the blue dashed line is the relationship fit by
    the phylogenetic mixed-effects
  model.}{\includegraphics[width=\textwidth]{diversity_range_bodymass.pdf}}\label{figsupp:div-range-bodymass}

   \figsupp{Pairwise diversity grouped by the range categories from
    \cite{Leffler2012-zj}, with point size indicating the predicted population
    density. The vertical lines are the range category group
  means.}{\includegraphics{diversity_leffler_ranges.pdf}}\label{figsupp:div-leffler}
  \end{fullwidth}
\figdata{The diversity and population size dataset for 172 metazoan taxa.}
\end{figure}

@@

\begin{figure}
  \begin{fullwidth}
  \includegraphics[width=\linewidth]{diversity_pcm.pdf}

@@

  \figsupp{The posterior distributions for the parameters of the phylogenetic
    mixed-effects model of diversity and population size (this is analogous to
    Figure \FIG{pcm}B) fit separately on chordates ($n=68$), molluscs
    ($n=13$), and arthropods ($n=68$). The phylogenetic mixed-effects model for
    chordates indicated the best-fitting model had no residual variance
    ($\sigma_r^2 = 0$), so an alternate model without this variance component
    was used to ensure proper convergence; this model is shown in green.
    The light blue (green) shaded regions are the 90\% credible intervals, the
    blue (green) lines the posterior averages, the gray shaded regions the OLS
    bootstrap 95\% confidence intervals, and the gray lines the OLS estimate.
    Note that unlike \FIG{pcm}, the OLS estimate uses all taxa,
    not just those present in the phylogeny, since splitting the data by phyla
    reduces sample sizes (OLS with just the subset of taxa in the phylogeny is
    not significant for either chordates and arthropods). The vertical dashed
  gray line indicates zero.}{\includegraphics[width=\textwidth]{div_popsize_post_phyla.pdf}}\label{figsupp:div-popsize-post-phyla}

  \figsupp{The ancestral continuous trait estimates for diversity and population size with species labels.}{\includegraphics[width=\textwidth]{biconmap_diversity.pdf}}\label{figsupp:anc-species}

  \figsupp{The ancestral continuous trait estimates for recombination map
  length and diversity and population size with species
labels.}{\includegraphics[width=\textwidth]{biconmap.pdf}}\label{figsupp:anc-maplen}

@@

\begin{figure}[t!]
  \begin{fullwidth}
  \includegraphics[width=\linewidth]{figure_3.pdf}

@@

  \figsupp{The relationship between genome size and approximate census
    population size. The dashed gray line indicates the OLS fit. Tiger
    salamander (\emph{Ambystoma tigrinum}) was excluded because of its
  exceptionally large genome size (~30Gbp).}{\includegraphics[width=\textwidth]{genome_size_popsize.pdf}}\label{figsupp:genome-size-Nc}

  \figsupp{The relationship between genome size and recombination map length.
    The dashed gray line indicates the OLS fit for all taxa, and the dashed
    colored dashed lines indicate the linear relationship fit by phyla. Tiger
    salamander (\emph{Ambystoma tigrinum}) was excluded because of its
  exceptionally large genome size (~30Gbp).}{\includegraphics[width=\textwidth]{genome_size_maplength.pdf}}\label{figsupp:genome-size-maplen}

  \figsupp[The relationship between $N_c$ and diversity in the
    \cite{Corbett-Detig2015-gt} data, and the relationship between estimated
    reduction in diversity and census size, for three different approaches.]{(A)
    The diversity data from \cite{Corbett-Detig2015-gt} and the census
    population size estimated here for metazoan taxa. (B) The reductions in
    diversity, $R = \nicefrac{N_e}{N}$, plotted against census size across
    species. The red points are the reductions estimated by
    \cite{Corbett-Detig2015-gt}. This confirms
    \citeauthor{Corbett-Detig2015-gt}'s (2015) finding that the impact of
    selection ($I = 1-R$) increases with census population size (though, in the
    original paper size body size and range were used as separate proxy
    variables for census population size). The green and red points are the
    predicted reduction in diversity under the recurrent hitchhiking (RHH) and
    background selection (BGS) model using the \emph{Drosophila melanogaster}
    parameters as described in the main text.  The reduction in the diversity
    due to sweeps, from Equation 1, is determined by the term
    $2NS$.  Green points treat $N$ as the implied effective population size
    from diversity $\widetilde{N}_e = \nicefrac{\widehat{\pi}}{4\mu}$, assuming
    $\mu = 10^{-9}$. Yellow points treat $N$ as the census size, $N = N_c$.
    Overall, using the census size, e.g.  $2N_cS$, leads to reductions in
    diversity that far exceed the empirical estimates of Corbett-Detig et al.
  and reasonable model-based predictions from
$\widetilde{N}_e$.}{\includegraphics[width=\textwidth]{corbett_detig.pdf}}\label{figsupp:reductions}

\figsupp{Comparison of the \emph{Drosophila} sweep parameters used in this study with parameters from other studies.
     (A) The estimate of the number of sweeps per basepair, per genome
      ($\nu_\text{BP}$) from Table 2 of \cite{Elyashiv2016-vt} (the studies
      included are \cite{Li2006-xa,Andolfatto2007-uy,Macpherson2007-qt} and
      \cite{Jensen2008-vz}); the red point is my estimate used in
      this paper. (B) Points are the data from \cite{Shapiro2007-gp}.  The
      blue line is the non-linear least squares fit to the data, and the green
      dashed line is the sweep model parameterized by the genome-wide average
      sweep coalescent rate $2NS \approx 0.92$ from the classic sweep and
      background selection model of \cite{Elyashiv2016-vt} ($r_s$ in
    Supplementary Table S6).}{\includegraphics[width=\textwidth]{linked_sel_params.pdf}}\label{figsupp:linked-sel-params}

@@

@@

\begin{figure}
  \includegraphics[width=\textwidth]{diversity_popsize_redlist.pdf}
  \captionof{figure}{A version of \FIG{pi-Nc} with points colored by their
    IUCN Red List conservation status. Margin boxplots show the diversity and
    population size ranges (thin lines) and interquartile ranges (thick lines)
    for each category. NA/DD indicates no IUCN Red List entry, or Red List
  status Data Deficient; LC is Least Concern, NT is Near Threatened, VU is
Vulnerable, EN is Endangered, and CR is Critically Endangered.}
\label{figsupp:figure-1-redlist}
\end{figure}
